Hypertension and microbiome

### 2019-01-23 articletwo.Rmd
Minoq

ggsave(file = "cache/alpha-beta.png", plot=g4, height=fig.height, width=11)

@@

pca.pc3.gg <- ggplot(data=pca.loading.pc3.top20, aes(x=reorder(name, -PC3), y=100*PC3)) +
    geom_bar(stat="identity", width=0.5, position = position_dodge(preserve = "single")) +
    theme_classic(20) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1)) +
    xlab("") +
    ylab("Contribution (%)") +
#    coord_fixed(ratio = 1) +
    theme(axis.title.x=element_blank(),
          text = element_text(size=20),
          legend.justification=c(1,0),
          legend.position=c(1.03, 0.75),
          legend.title=element_text(size = 20),
          legend.direction="vertical",
          legend.text=element_text(size = floor(0.75*20)),
          legend.box.margin = margin(1, 1, 1, 1, "mm"),
          legend.box.background = element_rect(colour = "black"),
          aspect.ratio = 0.7)
   ggsave(file = "cache/pca.pc3.png", plot = pca.pc3.gg, height = 8, width = 8, dpi = 300) 
```

>>>>

ggsave(file = "cache/alpha-beta.png", plot=g4, height=10, width=11)

@@

pca.pc3.gg <- ggplot(data=pca.loading.pc3.top20, aes(x=reorder(name, -PC3), y=100*PC3)) +
    geom_bar(stat="identity", width=0.5, position = position_dodge(preserve = "single")) +
    theme_classic(20) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.3, hjust = 1)) +
    xlab("") +
    ylab("Contribution (%)") +
    scale_y_continuous(limits=c(0, 2.7), oob = rescale_none, expand = c(0,0)) +
    theme(axis.title.x=element_blank(),
          text = element_text(size=20),
          legend.justification=c(1,0),
          legend.position=c(1.03, 0.75),
          legend.title=element_text(size = 20),
          legend.direction="vertical",
          legend.text=element_text(size = floor(0.75*20)),
          legend.box.margin = margin(1, 1, 1, 1, "mm"),
          legend.box.background = element_rect(colour = "black"),
          aspect.ratio = 0.7)
   ggsave(file = "cache/pca.pc3.png", plot = pca.pc3.gg, height = 8, width = 8, dpi = 300) 
```
